Balsa: A Compact Line Notation Based on SMILES

### 2022-07-01 manuscript.tex
Adds figure for PPB. closes #7

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Partial parity bond. Bond conformational parity is distributed over two or more bonds.}
    \label{fig:partial-parity-bonds}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{partial-parity-bond.pdf}
    \caption{Partial parity bond (PPB). Double bond conformational parity is distributed over at least three bonds. A minimal assembly contains a double bond, two flanking PPBs (marked with upward- or downward-facing arrows), and associated nodes (top). To determine 2D orientation, parent and child are arranged on a vertical axis with parent above child for a bond direction of Down, and child above parent for a bond direction of Up (bottom-left). A complete diagram places parent, child, grandchild and great-grandchild (bottom right).}
    \label{fig:partial-parity-bonds}
\end{figure}
